Sections and Chapters

### 2017-04-25 draft1_SM.tex
Update draft1_SM.tex

The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30. Figure~\ref{fig:OSY} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:OSY} summarizes the mean quality metrics for each algorithm for ten runs.
%\begin{figure}[h]
%  \caption{Example Pareto Results for OSY}
%  \centering
%  \includegraphics[width=0.85\textwidth]{OSY_pareto_final.png}  
%  \label{fig:OSY}
%\end{figure}

\begin{table}[h]
\caption{Quality Metrics for OSY} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD &  &   \\ \hline
OS &  &  \\ \hline
\end{tabular}
\label{tab:OSY} 
\end{table}

>>>>

The true Pareto frontier for this problem again occurs when $x_i$ = 0 for i = 2,...,30. Figure~\ref{fig:OSY} shows a sample result from both MATLABs built in MOGA and the MOGA developed in this project. Table~\ref{tab:OSY} summarizes the mean quality metrics for each algorithm for ten runs.
\begin{figure}[h]
  \caption{Example Pareto Results for OSY}
  \centering
  \includegraphics[width=0.85\textwidth]{OSY_pareto_final.png}  
  \label{fig:OSY}
\end{figure}

\begin{table}[h]
\caption{Quality Metrics for OSY} 
\centering 
\begin{tabular}{|c|c|c|} 
\hline\hline  
Metric & MATLABs MOGA & Our MOGA \\ \hline
CD & 0.7882 (0.1995) & 0.5507 (0.0685)  \\ \hline
OS & 0.5322 (0.3393) & 0.9608 (0.2427) \\ \hline
\end{tabular}
\label{tab:OSY} 
\end{table}

Overall, our MOGA outperformed MATLABs MOGA in both quality metrics. However, by examining the Pareto frontiers, it is clear that neither algorithm is truely satisfactory in estimating the true Pareto frontier.
